New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-02-08 paper/paper.tex
Small fix in the paper

Within R, the natural implementation for an interactive interface would
use \texttt{shiny} \citep{shinym} with \texttt{plotly} \citep{plotly}
drawing. However, the \texttt{plotly} package is designed to add to
\texttt{ggplot2} \citep{ggplot2} graphics, not to be a programmable
interactive graphics system. It lacks the capability to implement the
primary tool needed for a manual tour, which is the tracking of the
cursor position in small increments. In theory, the historical
\texttt{locator()} function of base R should provide the necessary
capability, but its behavior is not consistent between graphical
devices. The cursor position control is possible for 3D plots with
\texttt{rgl} \citep{rgl} and \texttt{plotly} but these not the arbitrary
dimension needed for tours. The level of interactivity would have been
possible with the \texttt{cranvas} system \citep{cranvas} or
\texttt{rJava} \citep{rJava} but neither has a graphics toolkit that
currently operates across platforms. What we have chosen to do is to use
the interactivity of Mathematica to experiment, and to implement the
resulting ideas as an animation in the \texttt{tourr} \citep{tourr}
package. There is hope that better interactivity will be available for R
soon, perhaps in javascript \citep[e.g.][\citet{detourr}]{langevitour},
which might allow for the experimentation to develop new techniques.

@@

\begin{itemize}
\tightlist
\item
  The Mathematica source code defining the new functions in mmtour.wl.
\item
  Two Mathematica notebooks with the code used in the application
  (corresponding to the three subsections).
\item
  Appendix with additional details about manual controls, and
  Mathematica functions.
\item
  Data files for the examples.
\item
  R code to reproduce the example data, Figures 1 and 2 in the paper and
  Figures 1 and 2 in the appendix.
\item
  Animations illustrating the manual tour and slicing are also available
  at \url{https://vimeo.com/747585410} and
  \url{https://vimeo.com/747590472}.
\end{itemize}

>>>>

Within R, the natural implementation for an interactive interface would
use \texttt{shiny} \citep{shinym} with \texttt{plotly} \citep{plotly}
drawing. However, the \texttt{plotly} package is designed to add to
\texttt{ggplot2} \citep{ggplot2} graphics, not to be a programmable
interactive graphics system. It lacks the capability to implement the
primary tool needed for a manual tour, which is the tracking of the
cursor position in small increments. In theory, the historical
\texttt{locator()} function of base R should provide the necessary
capability, but its behavior is not consistent between graphical
devices. The cursor position control is possible for 3D plots with
\texttt{rgl} \citep{rgl} and \texttt{plotly} but not for the arbitrary
dimension needed for tours. The level of interactivity would have been
possible with the \texttt{cranvas} system \citep{cranvas} or
\texttt{rJava} \citep{rJava} but neither has a graphics toolkit that
currently operates across platforms. What we have chosen to do is to use
the interactivity of Mathematica to experiment, and to implement the
resulting ideas as an animation in the \texttt{tourr} \citep{tourr}
package. There is hope that better interactivity will be available for R
soon, perhaps in javascript \citep[e.g.][\citet{detourr}]{langevitour},
which might allow for the experimentation to develop new techniques.

@@

\begin{itemize}
\tightlist
\item
  The Mathematica source code defining the new functions in mmtour.wl.
\item
  Two Mathematica notebooks with the code used in the application.
\item
  Appendix with additional details about manual controls, and
  Mathematica functions.
\item
  Data files for the examples.
\item
  R code to reproduce the example data, Figures 1 and 2 in the paper and
  Figures 1 and 2 in the appendix.
\item
  Animations illustrating the manual tour and slicing are also available
  at \url{https://vimeo.com/747585410} and
  \url{https://vimeo.com/747590472}.
\end{itemize}
